Product graphics

### 2009-11-30 product-graphics.tex
Minor updates

  \item {\bf spine}: width is proportional to value, height equally divides space. Splines are space filling, but make it more difficult to compare absolute counts.  Splines can be arranged horizontally (``hspline''),  vertically (``vspline''), or can automatically pick their orientation (``spline'').

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.33\linewidth]{part-hbar}%
    \includegraphics[width=0.33\linewidth]{part-hspline}
    % \includegraphics[width=0.25\linewidth]{part-treemap}

  \caption{1d partitions showing proportions 0.5, 0.2, 0.2 and 0.1. From left to right: horizontal bars, horizontal splines, and a treemap.}
  \label{fig:part-1d}
\end{figure}

@@

\begin{itemize}
  \item {\bf Barchart} (1d). 1 hbar.
  \item {\bf Column chart} (1d). 1 vbar.
  \item {\bf Spineplot} (1d). 1 vspline.

@@

  \item {\bf Equal bin size} plot (3d): fluct and vspline, provided the final two variables are uniform.

@@

\begin{itemize}

@@

    \includegraphics[width=0.25\linewidth]{hb-vb-polar}%
    \includegraphics[width=0.25\linewidth]{hb-vs-polar}%
    \includegraphics[width=0.25\linewidth]{hs-hs-polar}%
    \includegraphics[width=0.25\linewidth]{hs-vs-polar}
  \caption{(Top) Area graphics in Cartesian coordinates.  (Bottom) Area graphics in polar coordinates.  From left to right: horizontal bar nested inside horizontal bar, vertical spline nested inside horizontal bar (stacked bar chart), horizontal spline nested in horizontal spline, horizontal spline nested in vertical spline (mosaic plot).}
  \label{fig:polar}
\end{figure}

>>>>

  \item {\bf spine}: width is proportional to value, height equally divides space. Splines are space filling, but make it more difficult to compare absolute counts.  Splines can be arranged horizontally (``hspine''),  vertically (``vspine''), or can automatically pick their orientation (``spine'').

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.33\linewidth]{part-hbar}%
    \includegraphics[width=0.33\linewidth]{part-hspine}
    % \includegraphics[width=0.25\linewidth]{part-treemap}

  \caption{1d partitions showing proportions 0.5, 0.2, 0.2 and 0.1. From left to right: horizontal bars, horizontal spines, and a treemap.}
  \label{fig:part-1d}
\end{figure}

@@

\begin{itemize}
  \item {\bf Barchart} (1d). 1 hbar.
  \item {\bf Column chart} (1d). 1 vbar.
  \item {\bf Spineplot} (1d). 1 vspine.

@@

  \item {\bf Equal bin size} plot (3d): fluct and vspine, provided the final two variables are uniform.

@@

@@

    \includegraphics[width=0.25\linewidth]{hb-vb-polar}%
    \includegraphics[width=0.25\linewidth]{hb-vs-polar}%
    \includegraphics[width=0.25\linewidth]{hs-hs-polar}%
    \includegraphics[width=0.25\linewidth]{hs-vs-polar}
  \caption{(Top) Area graphics in Cartesian coordinates.  (Bottom) Area graphics in polar coordinates.  From left to right: horizontal bar nested inside horizontal bar, vertical spine nested inside horizontal bar (stacked bar chart), horizontal spine nested in horizontal spine, horizontal spine nested in vertical spine (mosaic plot).}
  \label{fig:polar}
\end{figure}
